Security on Networks

### 2013-05-16 paper/paper.tex
intro

As epidemics spread on computer, disease propagation, and financial networks, agents in the network often undertake costly investments in security to help protect themselves from infection. However, these investments are often imperfect and typically succeed with some finite probability less than one. Furthermore, the cost of a security investment and its probability of success both increase with the chosen level of security. Thus agents face a tradeoff between choosing high investment in security to minimize infection probability and choosing low investment in security to minimize cost.

\section{Static Infection Model}
d
Althoug modeling infection on the network dynamically with a model such as SIR is more representative of real epidemics, such a model is intractable for the purpose of theoretical reasoning. In this section, we utilize the static model of infection as described in unpublished work by Acemoglu et al. (2013). Specifically, we apply the network security game model to Erd\H{o}s-R\'{e}nyi random graphs. We characterize the difference in network infection rates between the case of actions chosen by rational utility-maximizing agents and the case of actions chosen to maximize total social welfare. This difference is significant, as it can be readily interpreted as the cost of anarchy in a society with interactions modeled by a random graph.

>>>>

As epidemics spread on computer, disease propagation, and financial networks, agents in the network often undertake costly investments in security to protect themselves from infection. However, these investments are often imperfect and typically succeed with some probability less than one. Furthermore, the cost of a security investment and its probability of success both increase with the chosen level of security. Thus agents face a tradeoff between choosing high investment in security to minimize infection probability and choosing low investment to minimize cost. Given the easily definable utility functions of agents, it is appropriate to model the choice of security as a game on a network.

In this paper, we extend the game theoretic framework developed in unpublished work from Acemoglu et al. to random graph models. We spend the majority of the paper considering the static model of infection in which each agent chooses a security level once before epidemic propagation. In the static infection model, we specifically concern ourselves with characterizing the difference in infection rates between the Nash equilibrium and the social optimum. We also discuss some simulation results on the dynamic model, in which agents observe the infection state of their $k$-neighborhood at each timestep and update their security investments accordingly. Finally, we present some results on the intractability of computing infection probabilities exactly, and we provide a fully polynomial time approximation scheme for arbitrarily small $\epsilon$.

\section{Static Infection Model}

Although modeling infection on the network dynamically with a model such as SIR is more representative of real epidemics, such a model is intractable for the purpose of theoretical reasoning. In this section, we utilize the static model of infection as described in unpublished work by Acemoglu et al. (2013). Specifically, we apply the network security game model to Erd\H{o}s-R\'{e}nyi random graphs. We characterize the difference in network infection rates between the case of actions chosen by rational utility-maximizing agents and the case of actions chosen to maximize total social welfare. This difference is significant, as it can be readily interpreted as the cost of anarchy in a society with interactions modeled by a random graph.
